---
title: "Reducing Stranded Assets through Early action in the Indian Power Sector"
author: "Aman Malik and Christoph Bertram"
output: 
  html_document:
    theme: paper
    toc: true
    toc_float:
      collapsed: false
---

```{r global_settings, include=FALSE}
# setting global settings for knitr
# echo=TRUE/FALSE whether to include R source code in the output file
knitr::opts_chunk$set(fig.path = "figure-carbonlockin/", cache = T, echo = F, fig.retina = 1, warning = F, message = F)
```

```{r req_packages,message=FALSE, warning=FALSE, include=FALSE,results='hide'}
library(quitte)
library(mrremind)
library(tidyverse)
library(reshape)
library(data.table)
library(RColorBrewer)
library(knitr)
library(mip)
library(readxl)
library(ggpubr)
```

<!-- ### Data preperation -->

```{r input_data_file}
load("Data/data_IND2019_08_12.RData")
models <- inline.data.frame(
  'model;                       model.name',
  'REMIND-MAgPIE 1.7-3.0;         REMIND',
  'WITCH2016;          WITCH',
  'AIM/Enduse 3.0;            AIM/Enduse',
  'IMAGE 3.0;     IMAGE',
  'POLES CDL;   POLES',
  'AIM V2.1; AIM',
  'India MARKAL; India MARKAL',
  'GEM-E3; GEM_E3',
  NULL
)

## Renaming model names
whole <- whole %>%
  replace_column(models, model, model.name) %>%
  order.levels(scen_name = c("Delayed action", "Early action")) %>%
  removeColNa() %>%
  order.levels(
    model = c(
      "AIM",
      "IMAGE",
      "POLES",
      "GEM_E3",
      "REMIND",
      "WITCH",
      "AIM/Enduse",
      "India MARKAL"
    )
  )



# Changing AIM/Enduse SE values for solar and wind based on excel sheet sent by Saritha

aim_npi_spv <-
  c(2.25,
    1.83,
    30.36,
    78.21,
    984.41,
    1558.15,
    1940.17,
    2229.42,
    2536.68,
    2475.69) / 1000 # converting from PJ to EJ

aim_ndc_spv <-
  c(2.25,
    1.83,
    30.36,
    81.53,
    385.54,
    973.31,
    1350.24,
    1881.97,
    2448.31,
    3051.37) / 1000
aim_npi_wind <-
  c(26.96,
    75.06,
    138.68,
    220.33,
    269.39,
    337.01,
    429.57,
    566.43,
    617.58,
    646.49) / 1000
aim_ndc_wind <-
  c(26.96,
    75.06,
    138.68,
    252.29,
    331.13,
    420.48,
    430.69,
    565.02,
    657.00,
    748.98) / 1000

whole[whole$model == "AIM/Enduse" &
        whole$variable == "Secondary Energy|Electricity|Solar" &
        whole$scen_name == "Early action",]$value <- aim_npi_spv

whole[whole$model == "AIM/Enduse" &
        whole$variable == "Secondary Energy|Electricity|Solar" &
        whole$scen_name == "Delayed action",]$value <- aim_ndc_spv

whole[whole$model == "AIM/Enduse" &
        whole$variable == "Secondary Energy|Electricity|Wind" &
        whole$scen_name == "Early action",]$value <- aim_npi_wind

whole[whole$model == "AIM/Enduse" &
        whole$variable == "Secondary Energy|Electricity|Wind" &
        whole$scen_name == "Delayed action",]$value <- aim_ndc_wind

# Changing AIM/Enduse values for Capacity|Solar
whole[whole$model == "AIM/Enduse" &
        whole$variable == "Capacity|Electricity|Solar",]$value <-
  whole[whole$model == "AIM/Enduse" &
          whole$variable == "Capacity|Electricity|Solar",]$value + whole[whole$model == "AIM/Enduse" &
                                                                           whole$variable == "Capacity|Electricity|Storage",]$value
```


#### India historical data
```{r historical_data}
load("Data/HistandBotmup.RData")

### historical data from various government sources: CEA reports, MNRE, NITI AAYOG
hist_IND <- readxl::read_excel("Data/Compiled_historical.xlsx")
hist_IND <- as.quitte(hist_IND)
```

<!-- #### Color palette -->

```{r}
## Specific colours for the model names
myColors <- brewer.pal(8, name = "Dark2") # for unique colors on models
names(myColors) <- getModels(whole)
```

<!-- #### Data wrangling for calculating stranded assets -->

```{r data_input_ch2_part2}
## Rescaling Secondary energy and converting to capacity

whole_se_elec_coal <- whole %>%
  filter(variable %in% c("Secondary Energy|Electricity|Coal|w/o CCS"), period %in% c(2020:2070), !is.na(scen_name))

whole_se_elec_coal_2020 <- whole %>%
  filter(variable %in% c("Secondary Energy|Electricity|Coal|w/o CCS"), period == 2020, scen_name == "Early action")

models <- unique(whole_se_elec_coal$model)

# Normalising SE values to values in 2020
for (i in models) {
  whole_se_elec_coal[whole_se_elec_coal$model == i, ]$value <- whole_se_elec_coal[whole_se_elec_coal$model == i, ]$value /
    whole_se_elec_coal_2020[whole_se_elec_coal_2020$model == i, ]$value
}
# setting all model's 2020 SE to 2020 SE (2018 CEA values + some captive capacity :  986591 + 147035.84=1133 GWh)
whole_se_elec_coal[whole_se_elec_coal$period == 2020, ]$value <- 4.22

whole_se_elec_coal[whole_se_elec_coal$period != 2020, ]$value <- 4.22 * whole_se_elec_coal[whole_se_elec_coal$period != 2020, ]$value

whole_se_elec_coal$value <- whole_se_elec_coal$value * 277777.778 # EJ to GWh
# converting SE to capacity using current capacity factor
whole_se_elec_coal$value <- whole_se_elec_coal$value / (8760 * 0.59) # GWh to GW using capacity factor in 2018

whole_coal_cap_resc <- whole_se_elec_coal
```

```{r data_input_ch2_part3}
#### Stranding capacity for early and delay scenarios

modelnames <- as.character(unique(whole_se_elec_coal$model))
df <- fread("Data/remaining_delay.csv", header = T)
df <- df %>% gather(2:41, key = "age", value = "capacity")
df$age <- as.numeric(df$age)
df$period <- 2030

df.REMIND <- df %>% filter(model == "REMIND")
shite.2 <- df.REMIND
for (i in 1:40) {
  df.blah <- df.REMIND %>%
    mutate(capacity = lag(capacity, i, order_by = age)) %>%
    mutate(period = period + i)
  shite.2 <- bind_rows(shite.2, df.blah)
}
shite.2 <- shite.2 %>%
  mutate(age_group = ifelse(age < 10, "0-9", ifelse(age >= 10 & age < 20, "10-19", ifelse(age >= 20 & age < 30, "20-29", ifelse(age >= 30 & age <= 40, "30-39", "NA")))))


shite.2$age_group <- factor(shite.2$age_group, levels = c("30-39", "20-29", "10-19", "0-9"))
shite.2[is.na(shite.2)] <- 0
# finding age group of stranded capacity
shite.2.try <- shite.2 %>%
  group_by(model, period, age_group) %>%
  summarise(vals = sum(capacity))
stranded <- data.frame(model = character(0), period = numeric(0), age_group = character(0), vals = numeric(0))
model.data <- whole_se_elec_coal %>%
  filter(period %in% c(2030:2060), scen_name == "Delayed action", model == "REMIND") %>%
  select(1, 6, 10)

# interpolate model data
model.data <- interpolate_missing_periods(model.data, seq(2030, 2050, 1))
ages <- unique(shite.2$age_group)
for (i in seq(2030, 2050, 1)) {
  if (model.data[model.data$period == i, ]$value < shite.2.try[shite.2.try$age_group == "0-9" & shite.2.try$period == i, ]$vals & shite.2.try[shite.2.try$age_group == ages[1] & shite.2.try$period == i, ]$vals != 0) {
    stranded <- bind_rows(stranded, data.frame(model = "REMIND", period = i, age_group = ages[1], vals = shite.2.try[shite.2.try$age_group == "0-9" & shite.2.try$period == i, ]$vals - model.data[model.data$period == i, ]$value), shite.2.try %>% filter(age_group != j & period == i))
  } else if (model.data[model.data$period == i, ]$value < sum(shite.2.try[shite.2.try$age_group %in% ages[1:2] & shite.2.try$period == i, ]$vals) & shite.2.try[shite.2.try$age_group == ages[2] & shite.2.try$period == i, ]$vals != 0) {
    stranded <- bind_rows(stranded, data.frame(model = "REMIND", period = i, age_group = ages[2], vals = as.numeric(shite.2.try %>% filter(period == i, age_group %in% ages[1:2]) %>% group_by(period) %>% summarise(vals = sum(vals)))[2] - model.data[model.data$period == i, ]$value), shite.2.try %>% filter(age_group %in% ages[3:4] & period == i))
  } else if (model.data[model.data$period == i, ]$value < sum(shite.2.try[shite.2.try$age_group %in% ages[1:3] & shite.2.try$period == i, ]$vals) & shite.2.try[shite.2.try$age_group == ages[3] & shite.2.try$period == i, ]$vals != 0) {
    stranded <- bind_rows(stranded, data.frame(model = "REMIND", period = i, age_group = ages[3], vals = sum(shite.2.try[shite.2.try$age_group %in% ages[1:3] & shite.2.try$period == i, ]$vals) - model.data[model.data$period == i, ]$value), shite.2.try %>% filter(age_group %in% ages[4] & period == i))
  } else if (model.data[model.data$period == i, ]$value < sum(shite.2.try[shite.2.try$age_group %in% ages[1:4] & shite.2.try$period == i, ]$vals) & shite.2.try[shite.2.try$age_group == ages[4] & shite.2.try$period == i, ]$vals != 0) {
    stranded <- bind_rows(stranded, data.frame(model = "REMIND", period = i, age_group = ages[4], vals = sum(shite.2.try[shite.2.try$age_group %in% ages[1:4] & shite.2.try$period == i, ]$vals) - model.data[model.data$period == i, ]$value))
  } else if (model.data[model.data$period == i, ]$value > sum(shite.2.try[shite.2.try$age_group %in% ages[1:4] & shite.2.try$period == i, ]$vals)) {
    stranded <- bind_rows(stranded, data.frame(model = "REMIND", period = i, age_group = ages[4], vals = 0))
  }
}
##################################################

###### Early action
df <- fread("Data/remaining_early.csv", header = T)
# df$model <- modelnames[-5]
df <- df %>% select(1:41)
# assuming all plants older than 40 years are retired in 2020
df <- df %>% gather(2:41, key = "age", value = "capacity")
df$age <- as.numeric(df$age)

df.REMIND <- df %>% filter(model == "REMIND")
df.REMIND$period <- 2020

shite <- df.REMIND
for (i in 1:40) {
  df.blah <- df.REMIND %>%
    mutate(capacity = lag(capacity, i, order_by = age)) %>%
    mutate(period = period + i)
  shite <- bind_rows(shite, df.blah)
}
shite <- shite %>%
  mutate(age_group = ifelse(age < 10, "0-9", ifelse(age >= 10 & age < 20, "10-19", ifelse(age >= 20 & age < 30, "20-29", ifelse(age >= 30 & age < 40, "30-39", "NA")))))


shite$age_group <- factor(shite$age_group, levels = c("30-39", "20-29", "10-19", "0-9"))
```

```{r data_input_ch2_part4}
indian_coal <- read_excel("Data/india_coal_2.xlsx")
ic <- indian_coal %>%
  gather(2:54, value = "value", key = "period")
colnames(ic)[1] <- "category"
ic$model <- "CEA"
ic$period <- as.integer(ic$period)
ic$scen_name <- "Projections"


# Data from Global Energy Monitor
input.data <-
  read_excel("Data/Coal_Swarm_INDIA.xlsx")

input.data <- input.data %>%
  gather(key = "Year", value = "Status", 4:8) %>%
  filter(Status != "XXX")

input.data$Status <-
  gsub("Pre|Perm|Ann", replacement = "Planned", input.data$Status)
input.data$Status <-
  gsub("She|Can", replacement = "Cancelled", input.data$Status)
input.data$Status <-
  gsub("Oper", replacement = "Operating", input.data$Status)
input.data$Status <-
  gsub("Ret", replacement = "Retired", input.data$Status)
input.data$Status <-
  gsub("Con", replacement = "Construction", input.data$Status)

input.data.2 <-
  input.data %>%
  group_by(Year, Status) %>%
  summarise(sum = sum(Capacity))
input.data.2 <- data.frame(input.data.2)
input.data.2$Year <- as.numeric(input.data.2$Year)

# Historical capacity
hist_IND <- readxl::read_excel("Data/Compiled_historical.xlsx")
hist_IND <- as.quitte(hist_IND)
```


### Fig. 1: Power generation from coal in 2030 Delayed action
```{r data_wrangling}

hist_se_elec_coal <- hist_and_botmup %>% filter(region == "IND", period %in% c(2005:2015), variable == "SE|Electricity|Coal (EJ/yr)")


wholeCoal <- whole %>%
  filter(variable %in% c("Secondary Energy|Electricity|Coal|w/o CCS")) %>%
  select(model, scen_name, value, period) %>%
  spread(scen_name, value = value) %>%
  mutate(difference = `Early action` - `Delayed action`) %>%
  gather(3:5, key = "scen_name", value = "value") %>%
  mutate(scen_name = factor(scen_name, levels = c("Delayed action", "Early action", "difference"))) %>%
  mutate(model_scope = if_else(model %in% c("AIM/Enduse", "India MARKAL"), "national", "global"))



whole_se_elec_coal_global <-whole %>%
  filter(variable %in% c("Secondary Energy|Electricity|Coal|w/o CCS")) %>%
  filter(period < 2051, scen_name == "Delayed action", model != "GEM_E3") %>%
  group_by(period, model_scope) %>%
  summarise(minimum = min(value) * 277.78, maximum = max(value) * 277.78)
```

```{r plotting}
p <- ggplot() +
  ### grey lines
  geom_line(data = wholeCoal %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "global"), aes(x = period, y = value * 277.78, group = interaction(model, scen_name)), size = 0.1, color = "grey", show.legend = F) +
  ## grey ribbon
  geom_ribbon(whole_se_elec_coal_global %>% filter(period %in% c(2010:2030), model_scope == "global"),
    mapping = aes(x = period, ymin = minimum, ymax = maximum, fill = model_scope), alpha = 0.5, fill = "grey", show.legend = F
  ) +
  ## national models dashed line
  geom_line(data = wholeCoal %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "national"), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model), linetype = 2, size = 1.5) +
  # Govt. projections
  geom_point(hist_IND %>% filter(variable == "Secondary Energy|Electricity|Coal", model %in% c("CEA_NEP", "IESS", "IEM", "CEA_OPT")), mapping = aes(x = period, y = value * 0.001, shape = model), color = "blue") +
  # Govt. historical
  geom_point(hist_IND %>% filter(variable == "Secondary Energy|Electricity|Coal", model == "CEA_growth"), mapping = aes(x = period, y = value * 0.001, size = scenario)) +
  ## Model names on right in light grey
  geom_text(wholeCoal %>% filter(period == 2030, scen_name == "Delayed action", model_scope == "global") %>% mutate(short_name = substring(model, 1, 1)), mapping = aes(x = 2030.5, y = value * 277.78, label = short_name, fontface = "bold"), color = "grey", size = 3) +
  scale_size_manual(values = c(1.5, 2.5)) +
  labs(
    y = "Power generation from coal w/o CCS (TWh)",
    size = ""
  ) +
  scale_colour_manual(values = myColors, limits = c("AIM/Enduse", "India MARKAL")) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 12),
    axis.text = element_text(size = 10),
    axis.title.x = element_blank(),
    strip.text.x = element_text(size = 8),
    axis.text.x = element_text(angle = 90, hjust = 1)
  )
p
```

### Fig. 2: Power generation from solar and wind in 2030 in Delayed action
```{r solar_wind,message=FALSE,warning=FALSE}

## Solar
whole_se_solar <- whole %>% filter(variable %in% c("Secondary Energy|Electricity|Solar"))

whole_se_solar_global <- whole_se_solar %>%
  filter(period < 2051, model_scope == "global", scen_name == "Delayed action", model != "GEM_E3") %>%
  group_by(period) %>%
  summarise(minimum = min(value) * 277.78, maximum = max(value) * 277.78)


q <- ggplot() +
  ## Grey lines
  geom_line(data = whole_se_solar %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "global"), mapping = aes(x = period, y = value * 277.78, group = interaction(model, scen_name)), size = 0.1, color = "grey") +
  ## Grey ribbons
  geom_ribbon(whole_se_solar_global %>% filter(period %in% c(2010:2030)), mapping = aes(x = period, ymin = minimum, ymax = maximum), alpha = 0.4, fill = "grey") +
  ## national models colored dashed
  geom_line(data = whole_se_solar %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "national"), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model), size = 1.5, linetype = 2) +
  ## historical and projections
  geom_point(hist_IND %>% filter(variable == "Secondary Energy|Electricity|Solar", model %in% c("CEA_MON", "CEA_ANNUAL", "CEA_NEP", "Prayas"), period %in% c(2010:2027)), mapping = aes(x = period, y = value, shape = scenario)) +
  ## Grey model names on right
  geom_text(whole_se_solar %>% filter(period == 2030, scen_name == "Delayed action", model_scope == "global") %>% mutate(short_name = substring(model, 1, 1)), mapping = aes(x = 2030.5, y = value * 277.78, label = short_name, fontface = "bold"), color = "grey", size = 3.5) +
  coord_cartesian(ylim = c(0, 460)) +
  labs(
    y = "Power generation from solar (TWh)"
  ) +
  scale_colour_manual(values = myColors, limits = c("AIM/Enduse", "India MARKAL")) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 14),
    axis.title.x = element_blank()
  )

q
##### Wind

whole_se_wind <- whole %>% filter(variable %in% c("Secondary Energy|Electricity|Wind"))

whole_se_wind_global <- whole_se_wind %>%
  filter(period < 2051, model_scope == "global", scen_name == "Delayed action", model != "GEM_E3") %>%
  group_by(period) %>%
  summarise(minimum = min(value) * 277.78, maximum = max(value) * 277.78)


r <- ggplot() +
  ## Grey lines
  geom_line(data = whole_se_wind %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "global"), mapping = aes(x = period, y = value * 277.78, group = interaction(model, scen_name)), size = 0.1, color = "grey") +
  ## Grey ribbons
  geom_ribbon(whole_se_wind_global %>% filter(period %in% c(2010:2030)), mapping = aes(x = period, ymin = minimum, ymax = maximum), alpha = 0.4, fill = "grey") +
  ## national models colored dashed
  geom_line(data = whole_se_wind %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "national"), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model), size = 1.5, linetype = 2) +
  ## historical and projections
  geom_point(hist_IND %>% filter(variable == "Secondary Energy|Electricity|Wind", model %in% c("CEA_MON", "CEA_ANNUAL", "CEA_NEP", "Prayas"), period %in% c(2010:2027)), mapping = aes(x = period, y = value, shape = scenario)) +
  ## Grey model names on right
  geom_text(whole_se_wind %>% filter(period == 2030, scen_name == "Delayed action", model_scope == "global") %>% mutate(short_name = substring(model, 1, 1)), mapping = aes(x = 2030.5, y = value * 277.78, label = short_name, fontface = "bold"), color = "grey", size = 3.5) +
  coord_cartesian(ylim = c(0, 460)) +
  labs(
    y = "Power generation from Wind (TWh)"
  ) +
  scale_colour_manual(values = myColors, limits = c("AIM/Enduse", "India MARKAL")) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 14),
    axis.title.x = element_blank()
  )

r
```


### Fig. 3: Power generation from gas in 2030 in Delayed action
```{r}
whole_se_gas <- whole %>% filter(variable %in% c("Secondary Energy|Electricity|Gas"))

whole_se_gas_global <- whole_se_gas %>%
  filter(period < 2051, model_scope == "global", scen_name == "Delayed action") %>%
  group_by(period) %>%
  summarise(minimum = min(value) * 277.78, maximum = max(value) * 277.78)


t <- ggplot() +
  ## Grey lines
  geom_line(data = whole_se_gas %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "global"), mapping = aes(x = period, y = value * 277.78, group = interaction(model, scen_name)), size = 0.1, color = "grey") +
  ## Grey ribbons
  geom_ribbon(whole_se_gas_global %>% filter(period %in% c(2010:2030)), mapping = aes(x = period, ymin = minimum, ymax = maximum), alpha = 0.4, fill = "grey") +
  ## national models colored dashed
  geom_line(data = whole_se_gas %>% filter(period %in% c(2010:2030), scen_name == "Delayed action", model_scope == "national"), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model), size = 1.5, linetype = 2) +
  ## historical and projections
  geom_point(hist_IND %>% filter(variable == "Secondary Energy|Electricity|Gas", model %in% c(
    "NITI AAYOG",
    "CEA_NEP"
  )), mapping = aes(x = period, y = value * 0.001, shape = scenario)) +
  ## Grey model names on right
  geom_text(whole_se_gas %>% filter(period == 2030, scen_name == "Delayed action", model_scope == "global") %>% mutate(short_name = substring(model, 1, 1)), mapping = aes(x = 2030.5, y = value * 277.78, label = short_name, fontface = "bold"), color = "grey", size = 3.5) +
  coord_cartesian(ylim = c(0, 800)) +
  labs(
    y = "Power generation from Gas (TWh)"
  ) +
  scale_colour_manual(values = myColors, limits = c("AIM/Enduse", "India MARKAL")) +
  theme_bw() +
  theme(
    axis.title = element_text(size = 14),
    axis.text = element_text(size = 14),
    axis.title.x = element_blank()
  )

t
```


### Fig. 4: Coal capacity development: natural-retirement pathway and stranded capacity

```{r}
strandDelayed <- ggplot() +
  geom_bar(shite.2, mapping = aes(x = period, y = capacity, fill = age_group), stat = "identity") +
  geom_line(data = whole_se_elec_coal %>% filter(period %in% c(2020:2060), scen_name == "Delayed action", model == "REMIND"), aes(x = period, y = value)) +
  scale_fill_manual(values = brewer.pal(n = 4, name = "YlOrRd")) +
  labs(
    x = "Year",
    y = "Coal Capacity (GW)",
    subtitle = "Delayed action-REMIND"
  ) +
  coord_cartesian(ylim = c(0, 340)) +
  theme_bw() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank())

strandEarly <- ggplot() +
  geom_bar(shite, mapping = aes(x = period, y = capacity, fill = age_group), stat = "identity") +
  geom_line(data = whole_se_elec_coal %>% filter(period %in% c(2020:2060), scen_name == "Early action", model == "REMIND"), aes(x = period, y = value, group = interaction(model, scen_name))) +
  labs(
    x = "Year",
    y = "Coal Capacity (GW)",
    subtitle = "Early action-REMIND"
  ) +
  scale_fill_manual(values = brewer.pal(n = 4, name = "YlOrRd")) +
  coord_cartesian(ylim = c(0, 340)) +
  theme_bw() +
  theme(axis.text = element_text(size = 10), axis.title.x = element_blank())

strandDelayed
strandEarly
```

### Fig. 5: Power generation mix in 2030, early and delayed action and the difference
```{r}
plotvar_2 <- c(#"Secondary Energy|Electricity|Biomass|w/ CCS",
             #"Secondary Energy|Electricity|Biomass|w/o CCS",
             "Secondary Energy|Electricity|Hydro",
             "Secondary Energy|Electricity|Nuclear",
             "Secondary Energy|Electricity|Solar",
             "Secondary Energy|Electricity|Wind",
             "Secondary Energy|Electricity|Gas|w/ CCS",
             "Secondary Energy|Electricity|Gas|w/o CCS",
             "Secondary Energy|Electricity|Coal|w/ CCS",
             "Secondary Energy|Electricity|Coal|w/o CCS",
             NULL)

wholeSeAll<- whole %>%
  filter(variable %in% plotvar_2) %>%
  select(model, scen_name, value, period, variable) %>%
  spread(scen_name, value = value) %>%
  mutate(difference = `Early action` - `Delayed action`) %>% 
  gather(4:6, key = "scen_name", value = "value") %>%
  mutate(scen_name = factor(scen_name, levels = c("Delayed action", "Early action", "difference"))) %>%
  mutate(model_scope = if_else(model %in% c("AIM/Enduse", "India MARKAL"), "national", "global"))

ggplot() +
  geom_bar(data = wholeSeAll %>% filter(period == 2030), aes(x = scen_name, y = value * 277.78, group = variable, fill = variable), position = "stack", stat = "identity") +
  facet_grid(. ~ model, labeller = label_wrap_gen(6, multi_line = TRUE)) +
  theme_bw()+
  theme(strip.text.x = element_text(size = 6), axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    x = "",
    y = "Power Generation in 2030 (TWh) "
  ) +
  scale_fill_manual(values = mip::plotstyle(plotvar_2))

```

### Fig. 6 Illustrative coal pathways

```{r}
remind <- whole_se_elec_coal %>%
  filter(variable == "Secondary Energy|Electricity|Coal|w/o CCS", model == "REMIND", period %in% c(2020:2070)) %>%
  select(1, 6, 9, 10)

natural <- ic %>% filter(category %in% c("Sum (operating)", "Sum (op+construction)"))

remind_natural_2030 <- shite.2 %>%
  group_by(period, model) %>%
  summarise(total = sum(capacity))

v <- ggplot() +
  ## early and delayed action from Remind
  geom_line(remind, mapping = aes(x = period, y = value, group = scen_name, color = scen_name), linetype = "dashed")+
  # natural retirement pathway for plants currently operating and op + under-construction
  geom_line(natural %>% filter(period > 2018), mapping = aes(x = period, y = value, group = category, color = category)) +
  # natural retirement path for early and delayed action
  geom_line(remind_natural_2030, mapping = aes(x = period, y = total, color = model)) +
  # historical data
    geom_line(input.data.2 %>% filter(Status == "Operating", Year > 2015), mapping = aes(x = Year, y = sum / 1000), color = "black")+
  ##historical data
    geom_line(hist_IND %>% filter(variable == "Capacity|Electricity|Coal", model == "NITI AAYOG", period < 2016), mapping = aes(x = period, y = value / 1000), color = "black")+
  scale_color_brewer(palette = "Dark2") +
   labs(y = "Coal Capacity (GW)") +
   theme_bw() +
  theme(axis.title.x = element_blank())
v
```


### Fig. S1
Made using tableau

### Fig. S2
Made using tableau

### Fig. S3


### Fig. S4: Final Energy of Electricity
```{r}
whole_fe_elec <- whole %>% filter(variable == "Final Energy|Electricity")

# Historical FE
hist_fe_elec <- hist_and_botmup %>% filter(region == "IND", period %in% c(2005:2015), variable == "FE|Electricity (EJ/yr)")


ggplot() +
  geom_line(data = whole_fe_elec %>% filter(period %in% c(2010:2050)), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model, linetype = model_scope, size = model_scope)) +
    facet_grid(scen_name~.)+
  labs(
    x = "Year",
    y = "Final Energy of Electricity (TWh)",
 #   title = "Delayed action"
  ) +
  theme_bw() +
  geom_point(hist_IND %>% filter(variable == "Final Energy|Electricity", model %in% c("CEA_growth", "CEA_EXEC")), mapping = aes(y = value * 0.001, x = period, shape = scenario)) +
  scale_size_manual(values = c(1, 1.5))+
  scale_colour_manual(values = myColors)
```

### Fig. S5: Price of Power Generation

```{r}
whole_ep <- whole %>% filter(variable == "Price|Secondary Energy|Electricity", period %in% c(2010:2100))

ggplot() +
  geom_line(data = whole_ep %>% filter(period %in% c(2010:2050)), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model, linetype = model_scope, size = model_scope)) +
    facet_grid(scen_name~.)+
  labs(
    x = "Year",
    y = "Price of Power generation (USD2010/GJ)",
 #   title = "Delayed action"
  ) +
  theme_bw() +
  scale_size_manual(values = c(1, 1.5)) +
  scale_colour_manual(values = myColors)

```

Fig. S6: Population
```{r}
pop <- whole %>% filter(variable == "Population",
                        scen_name =="Early action")
ggplot() +
  geom_line(data = pop %>% filter(period %in% c(2010:2050)), aes(x = period, y = value * 277.78, color = model, linetype = model_scope, size = model_scope)) +
  labs(
  #  x = "Year",
    y = "Population",
  ) +
  theme_bw() +
   scale_size_manual(values = c(1, 1.5)) +
  scale_colour_manual(values = myColors)

```

### Fig. S7: GDP in Market Exchange Rate (USD billion 2010)
```{r}
loc <- 0.015 # https://www.xe.com/currencycharts/?from=INR&to=USD&view=10Y

whole_gdp <- whole %>% filter(variable == "GDP|MER", period %in% c(2010:2050), scen_name == "Delayed action")
whole_gdp[whole_gdp$model_scope == "national", ]$value <- whole_gdp[whole_gdp$model_scope == "national", ]$value * loc

ggplot() +
  geom_line(data = whole_gdp %>% filter(scen_name == "Delayed action"), aes(x = period, y = value, color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  # facet_grid(scen_name~.)+
  theme_bw() +
  scale_colour_manual(values = myColors) +
  labs(y = "GDP|MER (billion US$2010)")
```

### Fig. S8: Final Energy
```{r}
whole_fe <- whole %>% filter(variable == "Final Energy", scen_name == "Delayed action")

ggplot() +
  geom_line(data = whole_fe %>% filter(period %in% c(2010:2050)), aes(x = period, y = value, color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  theme_bw() +
  scale_colour_manual(values = myColors) +
  labs(
    y = "Final Energy (EJ/yr)",
    x = "Year"
  )
```

### Fig. S9: Carbon Price
```{r}
whole_cp <- whole %>% filter(variable == "Price|Carbon", period %in% c(2010:2050), model_scope == "global")

ggplot() +
  geom_line(data = whole_cp, aes(x = period, y = value, color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  facet_grid(scen_name ~ .) +
  theme_bw() +
  scale_colour_manual(values = myColors, limits = unique(whole_cp$model)) +
  labs(y = "Carbon Price (US$2010/t CO2)", x = "")
# coord_cartesian(ylim=c(0,600))
```

### Fig. S10: Power generation from coal without CCS in early action
```{r}
wholeCoalEarly <- whole %>% filter(variable == "Secondary Energy|Electricity|Coal|w/o CCS", period %in% c(2005:2050))

ggplot() +
  geom_line(data = wholeCoalEarly %>% filter(scen_name == "Early action" ), aes(x = period, y = value, color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  # facet_grid(scen_name~.)+
  theme_bw() +
  scale_colour_manual(values = myColors) +
  labs(y = "Power generation from coal without CCS (TWh)")+
  coord_cartesian(xlim = c(2010,2030))

```
### Fig. S11: Emissions from energy and electricity sector

```{r}
## energy sector emissions
whole_emi <- whole[whole$variable == "Emissions|CO2|Energy", ]


ee <- ggplot() +
  geom_line(whole_emi %>% filter(period %in% c(2010:2050)), mapping = aes(x = period, y = value, group = interaction(modscen, variable), color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  facet_grid(scen_name ~ .) +
  geom_point(hist_and_botmup %>% filter(region == "IND", period %in% c(2010:2015), variable == "Emi|CO2|Energy (Mt CO2/yr)"), mapping = aes(x = period, y = value, shape = scenario)) +
  labs(
    x = "",
    y = "Emissions from Energy sector (Mt CO2/yr)"
  ) +
  theme_bw() +
  scale_colour_manual(values = myColors)

## electricity sector emissions
whole_emi_elec <- whole[whole$variable == "Emissions|CO2|Energy|Supply|Electricity", ]

ee2 <- ggplot() +
  geom_line(whole_emi_elec %>% filter(period %in% c(2010:2050)), mapping = aes(x = period, y = value, group = interaction(modscen, variable), color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  facet_grid(scen_name ~ .) +
  theme_bw() +
  geom_point(hist_and_botmup %>% filter(region == "IND", period %in% c(2010:2015), variable == "Emi|CO2|Energy|Supply|Electricity (Mt CO2/yr)"), mapping = aes(x = period, y = value, shape = scenario)) +
  labs(
    x = "",
    y = "Emissions from electricity sector (Mt CO2/yr)"
  ) +
  coord_cartesian(ylim = c(0, 2500)) +
  scale_colour_manual(values = myColors)

ggpubr::ggarrange(ee,ee2,nrow = 1,common.legend = T,legend = "right")

```


### Fig. S12 Cumulative emissions from 2016-2030
```{r}
### DATA
whole_emi_energy <- whole %>%
  filter(variable == "Emissions|CO2|Energy|Supply|Electricity", period %in% c(2015:2050)) %>%
  group_by(modscen) 

whole_emi_energy <- calcCumulatedDiscount(data = whole_emi_energy,nameVar ="Emissions|CO2|Energy|Supply|Electricity", discount = 0)

whole_emi_dem_tra <- whole %>%
  filter(variable == "Emissions|CO2|Energy|Demand|Transportation", scen_name != "NDC", period %in% c(2015:2050)) %>%
  group_by(modscen)

whole_emi_dem_tra <- calcCumulatedDiscount(whole_emi_dem_tra, nameVar = "Emissions|CO2|Energy|Demand|Transportation", discount = 0)


whole_emi_dem_ind <- whole %>%
  filter(variable == "Emissions|CO2|Energy|Demand|Industry", scen_name != "NDC", period %in% c(2015:2050)) %>%
  group_by(modscen)


whole_emi_dem_ind <- calcCumulatedDiscount(whole_emi_dem_ind, nameVar = "Emissions|CO2|Energy|Demand|Industry", discount = 0)

whole_emi_dem_res <- whole %>%
  filter(variable == "Emissions|CO2|Energy|Demand|Residential and Commercial", scen_name != "NDC", period %in% c(2015:2050)) %>%
  group_by(modscen)


whole_emi_dem_res <- calcCumulatedDiscount(whole_emi_dem_res, nameVar = "Emissions|CO2|Energy|Demand|Residential and Commercial", discount = 0)


whole_cum <- rbind(whole_emi_energy, whole_emi_dem_tra, whole_emi_dem_ind, whole_emi_dem_res)



whole_cum_2 <- whole_cum %>%
  spread(key = scen_name, value = value) %>%
  arrange(variable) %>%
  filter(period != 2010) %>%
  mutate(`Excess emissions` = `Delayed action` - lead(`Early action`, n = 8, default = `Delayed action`[1])) %>%
  gather(key = "scen_name", value = "value", c(9:11)) %>% 
  removeColNa() 

whole_cum_2$variable <- mip::shorten_legend(whole_cum_2$variable, maxchar = 20, identical_only = TRUE)

ggplot() +
  geom_bar(data = whole_cum_2 %>% filter(period == 2030), aes(x = scen_name, y = value / 1000, fill = variable, group = modscen), position = "stack", stat = "identity") +
  labs(
    x = "",
    y = "Cumulative Emissions (2016-2030) (Gt CO2)",
    fill = "Scenario Type",
    alpha = "Model Scope"
  ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid(~model, scales = "free", space = "free_x") +
  theme(strip.text.x = element_text(angle = 90, size = 8), axis.text.x = element_text(angle = 90, hjust = 1))
```

### Fig. S13: Capital Costs of Solar PV
```{r}
plotvar <- c("Capital Cost|Electricity|Solar|PV")
whole_cap_cost <- whole[whole$variable == plotvar, ]
localrate <- 0.02 # https://www.xe.com/currencycharts/?from=INR&to=USD&view=10Y
whole_cap_cost[whole_cap_cost$model %in% c("India MARKAL", "AIM/Enduse 3.0"), ]$value <- whole_cap_cost[whole_cap_cost$model %in% c("India MARKAL", "AIM/Enduse 3.0"), ]$value * localrate


ggplot() +
  geom_line(data = whole_cap_cost %>% filter(period %in% c(2010:2050), scen_name == "Delayed action"), aes(x = period, y = value, group = interaction(model, scen_name), color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  labs(
    y = "Capital Costs for Solar PV (USD2010/KW)",
    x = ""
  ) +
  scale_colour_manual(values = myColors, limits = unique(whole_cap_cost$model)) +
  theme_bw() +
  theme(axis.title = element_text(size = 12))
```
### Fig. S14: Coal capacity development, assuming natural retirement and colored according to age-group


### Fig. S15: Secondary Energy Hydro
```{r}
whole_sec_elec_hydro <- whole %>% filter(variable %in% c("Secondary Energy|Electricity|Hydro"))

hydro <- ggplot() +
  geom_line(data = whole_sec_elec_hydro %>% filter(period %in% c(2005:2030), scen_name == "Delayed action"), aes(x = period, y = value * 277.78, group = interaction(model, scen_name), color = model, linetype = model_scope, size = model_scope)) +
  # facet_grid(scen_name~.)+
  labs(
    x = "",
    y = "Power generation from Hydro (TWh)"
  ) +
  theme(strip.text.x = element_text(angle = 90, size = 8), axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_point(hist_IND %>% group_by(model, variable) %>% filter(variable == "Secondary Energy|Electricity|Hydro", model %in% c("CEA_NEP", "OWN"), period %in% c(2005:2027)), mapping = aes(x = period, y = value * 0.001, shape = scenario)) +
  scale_size_manual(values = c(1, 1.5)) +
  theme_bw() +
  scale_colour_manual(values = myColors)

whole_nuc <- whole %>% filter(variable == "Capacity|Electricity|Nuclear", scen_name == "Delayed action")


nuclear <- ggplot() +
  geom_line(data = whole_nuc %>% filter(period %in% c(2010:2050)), aes(x = period, y = value, color = model, linetype = model_scope, size = model_scope)) +
  scale_size_manual(values = c(1, 1.5)) +
  # facet_grid(scen_name~.)+
  geom_point(data = hist_IND %>% filter(variable == "Capacity|Electricity|Nuclear", model %in% c("CEA_ANNUAL", "CEA_NEP"), period %in% c(2010:2050)), mapping = aes(x = period, y = value / 1000, shape = scenario)) +
  coord_cartesian(ylim = c(0, 60), xlim = c(2010, 2030)) +
  theme_bw() +
  scale_colour_manual(values = myColors) +
  labs(
    y = "Nuclear Capacity (GW)",
    x = ""
  )

ggpubr::ggarrange(hydro, nuclear, common.legend = T, legend = "right")
``````
